\bf Range Analysis for the IonMonkey JavaScript engine

### 2012-05-02 project-writings/paper.tex
very minor nits

To summarize our evaluation, we discovered the checks we eliminate do result in
some measurable performance increase. In extremly short-running tests such
Sunspider (see Figure \ref{fig:sunspider}), the additional compile-time
overhead that our pass requires yields slightly slower performance.

@@

In order to get a different view of how well our optimization was
performing, we annotated IonMonkey to emit for each addition and subtraction
instruction compiled whether or not range analysis proved that it
could not overflow, and ran this against all of the tests in Kraken,
Sunspider, and v8bench. The data from these tests are presented in Figure
\ref{fig:count} (tests that were found to have very few total add
instructions were not included).

@@

These results show that our range analysis is generally quite
successful in eliminating overflow checks from programs, but our
timing results indicate that this does not yield that substantial of a
performance improvement. We believe that this is because the overhead
of an essentially never taken branch on modern hardware are quite
low. While on a microbenchmark we constructed overflow check
elimination resulted in a substantial (around 30\%) speedup, it appears that
this does not translate well to more realistic code.

@@

On a suite of standard Javascript benchmarks, our range analysis
succeeds in eliminating a large fraction of overflow checks for
integer additions and subtractions. This translates into a minor
overall performance win on the Kraken benchmark suite and a very minor
overall performance loss on the Sunspider suite. Since we should only
increase the quality of the generated code, any performance losses
should be from increased compilation overhead (Sunspider tests in
particular are quite short). The performance improvements are decent,
but not stellar; we believe this is because Javascript code is
generally not integer-arithmetic-heavy tight loops and because the
overflow test branches are generally predicted correctly.

A number of Further optimizations are possible using our range analysis
framework. If the range associated with an instruction becomes empty, then the
block has been proven dead and can be eliminated. Control flow operations can
be proven redundant as well, further eliminating computation and dead basic
blocks. These graph manipulations are currently not available in the IonMonkey
compiler, which is in active development but not yet complete. There are a
variety of reasons for this current design restriction. IonMonkey must
integrate very closely with the interpreter and the JS runtime, and so
generated code must maintain a careful correspondence with the interpreter.
This means that eliminating control flow is a non-trivial
operation\cite{dvander}.

>>>>

To summarize our evaluation, we discovered the checks we eliminate do result in
some measurable performance increase. In extremly short-running tests such
SunSpider (see Figure \ref{fig:sunspider}), the additional compile-time
overhead that our pass requires yields slightly slower performance.

@@

In order to get a different view of how well our optimization was
performing, we annotated IonMonkey to emit for each addition and subtraction
instruction compiled whether or not range analysis proved that it
could not overflow, and ran this against all of the tests in Kraken,
SunSpider, and v8bench. The data from these tests are presented in Figure
\ref{fig:count} (tests that were found to have very few total add
instructions were not included).

@@

These results show that our range analysis is generally quite
successful in eliminating overflow checks from programs, but our
timing results indicate that this does not yield that substantial of a
performance improvement. We believe that this is because the overhead
of an essentially never taken branch on modern hardware is quite
low. While on a microbenchmark we constructed overflow check
elimination resulted in a substantial (around 30\%) speedup, it appears that
this does not translate well to more realistic code.

@@

On a suite of standard Javascript benchmarks, our range analysis
succeeds in eliminating a large fraction of overflow checks for
integer additions and subtractions. This translates into a minor
overall performance win on the Kraken benchmark suite and a very minor
overall performance loss on the SunSpider suite. Since we should only
increase the quality of the generated code, any performance losses
should be from increased compilation overhead (SunSpider tests in
particular are quite short). The performance improvements are decent,
but not stellar; we believe this is because Javascript code is
generally not integer-arithmetic-heavy tight loops and because the
overflow test branches are generally predicted correctly.

A number of further optimizations are possible using our range analysis
framework. If the range associated with an instruction becomes empty, then the
block has been proven dead and can be eliminated. Control flow operations can
be proven redundant as well, further eliminating computation and dead basic
blocks. These graph manipulations are currently not available in the IonMonkey
compiler, which is in active development but not yet complete. There are a
variety of reasons for this current design restriction. IonMonkey must
integrate very closely with the interpreter and the JS runtime, and so
generated code must maintain a careful correspondence with the interpreter.
This means that eliminating control flow is a non-trivial
operation\cite{dvander}.
